### 2021-02-17 main.tex
Add some future work ideas
some additional future work

>>>>

Larger graphs

Joint model (trained jointly on predicate and function precedences)

Differentiate questions due to satiterations from questions due to success and failure

MS: Is there a knowledge transfer possible between related setups when we in vampire change
options (seemingly?) orthogonal to precedence (saturation algorithm, additional inference rules / reductions, AVATAR on/off,
clause selection strategies, etc.)?

KBO is a also parametrized by weights (along with the precedence). Could we learn those as well? (Jointly?)
